SNP Analysis

### 2018-09-14 snp/SNP_Prediction_Analysis.Rmd
adding exclusions for low SCA

@@

sample.info  = do.call(rbind.data.frame, sapply(qcdata$Samplename, strsplit, '_'))
colnames(sample.info) = c('PatientID','SampleID','EndoID','Level')
sample.info[] = lapply(sample.info[], as.character)
sample.info[which(sample.info$PatientID == 524 & sample.info$Level == 524), 'Level'] = ''
sample.info$Samplename = qcdata$Samplename

@@

sample.info = base::merge(sample.info, patient.info[,c('PatientID','Timepoint','Timepoint Code','Status','Pathology')], by.x=c('PatientID','EndoID'), by.y=c('PatientID','Timepoint Code'))

@@

patient.info = patient.info %>% rowwise() %>% dplyr::mutate( Endoscopy = ifelse(Timepoint == 'T1', 1, 2) )
```

@@

```{r, echo=F, warning=F, message=F}
qcdata$SampleType = 'BE'
qcdata$SampleType[grep('BLD',rownames(qcdata), ignore.case=T)] = 'Blood Normal'
qcdata$SampleType[grep('gastric',rownames(qcdata), ignore.case=T)] = 'Gastric Normal'
head(qcdata)

qcdata = base::merge(qcdata, sample.info[,c('PatientID','Samplename','Status','Timepoint','SCA.Ratio')], by='Samplename')

ggplot(subset(qcdata,SampleType == 'BE'), aes(Timepoint, SCA.Ratio, color=PatientID, group=Timepoint)) + geom_boxplot() + 
  facet_wrap(~Status, scales='free_x', ncol=2) + labs(title='SCA Ratio by Timepoint') + theme(legend.position = 'none')

ggplot(subset(qcdata,SampleType == 'BE'), aes(Timepoint, SCA.Ratio, color=PatientID, group=PatientID)) + geom_point() + geom_line() + 
  facet_wrap(~Status, scales='free_x', ncol=2) + labs(title='SCA Ratio by Timepoint') + theme(legend.position = 'none')

ggplot(qcdata, aes(round(Ploidy,2))) + geom_histogram() + 
  facet_wrap(~SampleType, scales='free', ncol=1) + labs(x='Ploidy', title='Ploidy, normal vs BE')

@@

ggplot(qcdata, aes(round(Ploidy,2), Purity, group=round(Ploidy,2), color=Status)) + geom_point() + 
  facet_wrap(~Status, scales='free', ncol=2) + labs(x='Ploidy', title='Ploidy vs Purity, normal vs BE')

#x=median(qcdata$SCA.Ratio,na.rm=T)+sd(qcdata$SCA.Ratio,na.rm=T)
x=0.01
y=median(qcdata$Purity,na.rm=T)-sd(qcdata$Purity,na.rm=T)/2

ggplot(qcdata, aes(Purity, SCA.Ratio, color=Status)) + geom_point() + 
         facet_wrap(~Status, ncol=1) + labs(title='Purity~SCA.Ratio, normal vs BE') + geom_vline(xintercept=y, color='grey')

ggplot(qcdata, aes(SCA.Ratio, Purity, color=Status)) + geom_point() + 
  facet_wrap(~Status) + labs(x='SCA', title='SCA vs Purity') + 
  geom_vline(xintercept = x, color='grey') + geom_hline(yintercept = y, color='grey')

table(subset(qcdata, Purity > y & SCA.Ratio < x & SampleType == 'BE')$Status)

@@

ggplot(qcdata, aes(SCA.Ratio, color=Status, fill=Status)) + facet_wrap(~Status, scales='free_y',nrow=1) +  geom_density(alpha=0.5) + labs(x='SCA Ratio', title='SCA Ratio, NP vs P')

summary(qcdata$SCA.Ratio)

ggplot(subset(qcdata, SampleType == 'BE'), aes(Purity, SCA.Ratio, color=Status)) + facet_grid(~Status) +
  geom_point() + geom_vline(xintercept = 0.5, color='darkgreen') + geom_hline(yintercept = 0.05, color='red') + 
  labs(title='Barretts only')

ggplot(subset(qcdata, SampleType == 'BE'), aes(Ploidy, SCA.Ratio, color=Status)) + facet_grid(~Status) + geom_point() + 
  geom_hline(yintercept = 0.03, color='red') + labs(title='Barretts only')

## PER ENDOSCOPY
qcdata.samples = qcdata %>% group_by(Samplename) %>% dplyr::mutate(
  PatientID = unlist(strsplit(Samplename, '_'))[1],
  EndoID = unlist(strsplit(Samplename, '_'))[3],
  Level = unlist(strsplit(Samplename, '_'))[4] 
)

qcdata = qcdata.samples %>% group_by(PatientID, EndoID, Status, Timepoint, SampleType) %>% dplyr::summarise(
  Ploidy = mean(Ploidy), Purity = mean(Purity), Goodnessoffit = mean(Goodnessoffit), SCA.Ratio = mean(SCA.Ratio)
)

## Low CN
lowPloidyCN = subset(qcdata, Status == 'P' & SampleType == 'BE' & SCA.Ratio <= 0.05 & Ploidy <= 2)

## samples have no apparent CN
noCN = subset(qcdata, Status == 'P' & SCA.Ratio <= 0 & SampleType == 'BE')

## high CN | ploidy, nonP
highPloidyCN = subset(qcdata, Status == 'NP' & SampleType == 'BE' & (SCA.Ratio >= mean(qcdata$SCA.Ratio,na.rm=T)+ sd(qcdata$SCA.Ratio,na.rm=T)*2 | Ploidy >= 2.7))

qcdata$SCA.Ratio = round(qcdata$SCA.Ratio, 4)

lowsca = subset(qcdata, Status == 'P' & SampleType == 'BE' & SCA.Ratio <= 0.05 & Ploidy <= 2)

@@

#### P: Low SCA, Ploidy<=2
`r round(nrow(lowPloidyCN)/nrow(subset(qcdata, Status == 'P' & SampleType == 'BE')), 3)*100`% of PROGRESSOR endoscopies have <5% SCA and an ASCAT ploidy of 2 or less. Most of these show a >90% purity as well.
`r pander(summary(lowPloidyCN$Purity))`

#### P: No SCA
`r round(nrow(noCN)/nrow(subset(qcdata, Status == 'P' & SampleType == 'BE')), 3)*100`% of PROGRESSOR endoscopies have 0 SCA

#### NP: High CN or ploidy > 2.3
`r round(nrow(highPloidyCN)/nrow(subset(qcdata, Status == 'NP' & SampleType == 'BE')), 3)*100`% of NON-PROGRESSOR samples have >2SD SCA (~25%) or high ploidy.

@@

# Adjust for ploidy
for (i in 1:nrow(mergedSegs)) {
  sample = rownames(mergedSegs)[i]
  x = unlist(strsplit(sample, '_'))
  ploidy = mean(subset(qcdata, SampleType == 'BE' & PatientID == x[1] & EndoID == x[2])$Ploidy)
  if (grepl('BLD|gastric', sample, ignore.case = T)) ploidy = 2
  mergedSegs[i,] = mergedSegs[i,]-(ploidy-1)
  mergedArms[i,] = mergedArms[i,]-(ploidy-1)
}

@@

```{r, echo=F, fig.height=12, fig.width=6}
## TODO: quantile normalize the SNP arrays by the sWGS values. 
# copy = do.call(cbind.data.frame,lapply(1:ncol(arrayDf), function(i) {
#   as.data.frame(normalize.quantiles.use.target(arrayDf[,i,drop=F], as.vector(allDf[,i])))
# }))
# 
# colnames(copy) = colnames(arrayDf)
# rownames(copy) = rownames(arrayDf)

grid.arrange(
  ggplot( melt(dysplasia.df), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, sWGS'),
  ggplot( melt(arrayDf), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP arrays'),
  #ggplot( melt(copy), aes(sample=value)) + stat_qq() + labs(title='Normal Q-Q plot, SNP arrays q-normed'),
  ncol=1
)
#arrayDf = as.matrix(copy)
```

@@

```{r, warning=F, fig.height=8}
qcdata.be = subset(qcdata, SampleType == 'BE')
get.qcinfo<-function(vec) {
  endo = vec[2]
  pt = vec[1]
  y = subset(qcdata.be, PatientID == pt & EndoID == endo)
  y = y %>% group_by(Status, Timepoint) %>%  dplyr::summarise( mean(Ploidy), mean(Purity), mean(Goodnessoffit), mean(SCA.Ratio) )
  cbind.data.frame('PatientID'=pt, 'EndoID'=endo, y, stringsAsFactors = F)
}

qc = do.call(rbind.data.frame, c( lapply(preds$Samplename[-pnr], function(x) get.qcinfo( unlist(strsplit(x, '_'))) ), stringsAsFactors=F))

pred.qc = cbind.data.frame(preds[-pnr,], qc)
#dim(pred.qc)
#table(pred.qc$Status)

grid.arrange(
  ggplot(pred.qc, aes(`mean(SCA.Ratio)`, Prob, color=Status)) + geom_point(),
  ggplot(pred.qc, aes(`mean(Ploidy)`, Prob, color=Status)) + geom_point(),
ncol=2)

pander(cor.test(pred.qc$`mean(SCA.Ratio)`, pred.qc$Prob), caption='Probability shows a 0.3 correlation with % of the genome altered')
```

@@

pred.qc = pred.qc %>% group_by(Status, PatientID) %>% dplyr::mutate(
  exclude=(Status == 'NP' & (length(which(Pathology == 'HGD')) > 0)),
  wgd = (Status == 'NP' & `mean(Ploidy)` > 2.7 )
)

@@

pred.qc = pred.qc %>% group_by(Status, Samplename) %>% dplyr::mutate(
  lowsca = ( `mean(SCA.Ratio)` < 0.03 & `mean(Purity)` >= 0.95)
)

ggplot(pred.qc, aes(`mean(SCA.Ratio)`, `mean(Purity)`, color=Status)) + geom_point() + facet_grid(~Status) + 
  geom_vline(xintercept=0.03) + geom_hline(yintercept = 0.95)

pander(
  rbind(rbind('n.Samples'=table(subset(pred.qc, !lowsca)$Status)),
  rbind('n.Patients'=table(unique(subset(pred.qc, !lowsca, select=c('PatientID','Status')))$Status))),
caption='Number of samples and patients that pass the low SCA:high purity thresholds')

@@

```{r echo=F}
pred.qc.ex = subset(pred.qc, !exclude & !wgd & !lowsca)
cuts = seq(0,1,0.1)

@@

@@

# per_pt = 
#   subset(pred.qc, !exclude) %>% group_by(PatientID, Status) %>% dplyr::summarise( max.Prob = max(Prob), max.RR = max(RR), max.Risk = max(Risk) )
# rocpp = pROC::roc(Status ~ max.Prob, data=per_pt, auc=T, ci=T, of='thresholds')
# roc.plot(rocpp) + labs(title='Max per patient - excluded HGD NP')

@@

table(subset(pred.qc, Risk == 'High' & !exclude & !lowsca & !wgd)$Status)/table(subset(pred.qc, !exclude & !lowsca & !wgd)$Status)
table(subset(pred.qc, Risk == 'Moderate' & !exclude & !lowsca & !wgd)$Status)/table(subset(pred.qc, !exclude & !lowsca & !wgd)$Status)
table(subset(pred.qc, Risk == 'Low' & !exclude & !lowsca & !wgd)$Status)/table(subset(pred.qc, !exclude & !lowsca & !wgd)$Status)

@@

ggplot(subset(pred.qc, !exclude & !wgd & !lowsca), aes(`mean(SCA.Ratio)`,Prob, color=Risk, shape=Status)) + 
  facet_grid(~Status) + geom_point()

ggplot(subset(pred.qc, !exclude & !wgd & !lowsca), aes(`mean(SCA.Ratio)`,Prob, color=Risk, shape=Status)) + 
  facet_grid(~Status) + geom_point()

@@

@@

ct = cor.test(pred.qc.ex$Prob, pred.qc.ex$`mean(SCA.Ratio)`)
ct2 = cor.test(pred.qc$Prob, pred.qc$`mean(SCA.Ratio)`)
```

@@

```{r loo, eval=F}

>>>>

qcdata = qcdata %>% rowwise %>% dplyr::mutate(
  PatientID = unlist(strsplit(Samplename, '_'))[1],
  SampleID = unlist(strsplit(Samplename, '_'))[2],
  EndoID = unlist(strsplit(Samplename, '_'))[3],
  Level = unlist(strsplit(Samplename, '_'))[4]
)
segments.list = lapply(segments.list, function(pt) {
  pt$sample = sub('\\.LogR','',pt$sample)
  pt
})

qcdata$ASCAT.SCA.ratio = apply(qcdata,1,function(s) {
  smp = subset(segments.list[[ s[['PatientID']] ]], sample == s[['Samplename']] & chr %in% c(1:22))
  smp = smp %>% rowwise %>% dplyr::mutate(
      #'Total' = nAraw + nBraw,
      'Total' = nMajor + nMinor,
      'CNV' = round(Total) - round(as.numeric(s[['Ploidy']])) )

  x = subset(smp, CNV != 0 & chr %in% c(1:22))
  sum(x$endpos - x$startpos) / chr.info[22,'genome.length']
})

qcdata$SampleType = 'BE'
qcdata$SampleType[grep('BLD',qcdata$Level, ignore.case=T)] = 'Blood Normal'
qcdata$SampleType[grep('gastric',qcdata$Level, ignore.case=T)] = 'Gastric Normal'

@@

sample.info = qcdata[,c('PatientID','SampleID','EndoID','Level','Samplename','ASCAT.SCA.ratio')]

@@

sample.info = base::merge(sample.info, patient.info[,c('PatientID','Timepoint','Timepoint Code','Status','Pathology')], by.x=c('PatientID','EndoID'), by.y=c('PatientID','Timepoint Code'))
head(sample.info)

@@

patient.info = patient.info %>% rowwise() %>% dplyr::mutate( Endoscopy = ifelse(Timepoint == 'T1', 1, 2) )

sample.info
ggplot(sample.info, aes(ASCAT.SCA.ratio, SCA.Ratio)) + geom_point() + facet_grid(~Status)

# ASCAT and Xiahong's estimates correlate in 86% of samples, that suggests that the 14% missing is due to the LOH I'm not trying to call
cor.test(sample.info$ASCAT.SCA.ratio, sample.info$SCA.Ratio)

@@

```{r, echo=F, warning=F, message=F}
qcdata = base::merge(qcdata, sample.info[,c('Samplename','Status','Timepoint','SCA.Ratio')], by='Samplename')

ggplot(qcdata, aes(Status, ASCAT.SCA.ratio, color=Status, group=Status)) + geom_boxplot() + facet_grid(~SampleType)

low = subset(qcdata, SampleType == 'BE' & ASCAT.SCA.ratio <= median(subset(qcdata, SampleType != 'BE')$ASCAT.SCA.ratio))

anno = cbind.data.frame(table(subset(qcdata, SampleType == 'BE' & ASCAT.SCA.ratio <= median(subset(qcdata, SampleType != 'BE')$ASCAT.SCA.ratio))$Status)/table(subset(qcdata, SampleType == 'BE')$Status))
colnames(anno) = c('Status','Ratio')
anno$label='median(normal SCA)'
anno$x = 0.4
anno$y = median(subset(qcdata, SampleType != 'BE')$ASCAT.SCA.ratio)

ggplot(subset(qcdata,SampleType == 'BE'), aes(Purity, ASCAT.SCA.ratio, color=Status, group=Status)) + geom_point() + facet_grid(~Status, scales = 'free') + ylim(0,0.005) + 
  geom_hline(yintercept = x) + geom_text(data=anno, aes(x, y, label=label), nudge_y = 0.0001) +
  geom_text(data=anno, aes(x, y, label=paste(round(Ratio,2)*100,'% samples',sep='')), nudge_y = -0.0001)

# ggplot(subset(qcdata,SampleType == 'BE'), aes(Timepoint, SCA.Ratio, color=PatientID, group=PatientID)) + geom_point() + geom_line() + 
#   facet_wrap(~Status, scales='free_x', ncol=2) + labs(title='SCA Ratio by Timepoint') + theme(legend.position = 'none')

ggplot(qcdata, aes(Ploidy, ASCAT.SCA.ratio, color=Status)) + geom_point() + facet_grid(~SampleType)

ggplot(qcdata, aes(Ploidy, ASCAT.SCA.ratio, color=Status)) + geom_point() + facet_grid(~Status)

ggplot(subset(qcdata,SampleType == 'BE'), aes(Timepoint, ASCAT.SCA.ratio, color=PatientID, group=Timepoint)) + geom_boxplot() + 
  facet_wrap(~Status, scales='free_x', ncol=2) + labs(title='SCA Ratio by Timepoint') + theme(legend.position = 'none')

ggplot(qcdata, aes(round(Ploidy,2))) + geom_histogram() + 
  facet_wrap(~SampleType, ncol=1) + labs(x='Ploidy', title='Ploidy, normal vs BE')

@@

#x=median(qcdata$SCA.Ratio,na.rm=T)+sd(qcdata$SCA.Ratio,na.rm=T)
x=0.05
y=median(qcdata$Purity,na.rm=T)-sd(qcdata$Purity,na.rm=T)/2

ggplot(qcdata, aes(Purity, ASCAT.SCA.ratio, color=ASCAT.SCA.ratio < 0.2)) + geom_point() + 
         facet_wrap(~Status, ncol=1) + labs(title='Purity~SCA.Ratio') + geom_vline(xintercept=y, color='grey')

ggplot(qcdata, aes(ASCAT.SCA.ratio, Purity, color=Status)) + geom_point() + 
  facet_wrap(~Status) + labs(x='SCA', title='SCA vs Purity') + 
  geom_vline(xintercept = x, color='grey') + geom_hline(yintercept = y, color='grey')

table(unique(subset(qcdata, Purity > y & ASCAT.SCA.ratio < x & SampleType == 'BE', select=c('Status','PatientID')))$Status)

@@

ggplot(qcdata, aes(ASCAT.SCA.ratio, color=Status, fill=Status)) + facet_wrap(~Status, scales='free_y',nrow=1) +  geom_density(alpha=0.5) + labs(x='SCA Ratio', title='SCA Ratio, NP vs P')

ggplot(qcdata, aes(ASCAT.SCA.ratio, color=Status, fill=Status)) + facet_wrap(Status~SampleType, scales='free_y',nrow=2) +  geom_density(alpha=0.5) + labs(title='SCA Ratio, NP vs P')

summary(subset(qcdata, SampleType == 'BE')$ASCAT.SCA.ratio)
summary(subset(qcdata, SampleType != 'BE')$ASCAT.SCA.ratio)

ggplot(subset(qcdata, SampleType == 'BE'), aes(Purity, ASCAT.SCA.ratio, color=Status)) + facet_grid(~Status) +
  geom_point() + geom_vline(xintercept = y, color='darkgreen') + geom_hline(yintercept = x, color='red') + 
  labs(title='Barretts only')

ggplot(subset(qcdata, SampleType == 'BE'), aes(Ploidy, ASCAT.SCA.ratio, color=Status)) + facet_grid(~Status) + geom_point() + 
  geom_hline(yintercept = 0.02, color='red') + labs(title='Barretts only')

## PER ENDOSCOPY
qcdata.endo = qcdata %>% group_by(PatientID, EndoID, Status, Timepoint, SampleType) %>% dplyr::summarise_if(is.numeric, c('mean','max','min','sd')) %>% mutate_if(is.numeric, round, digits=3)
qcdata %>% dplyr::group_by( Status, SampleType) %>% dplyr::summarise( median(ASCAT.SCA.ratio), sd(ASCAT.SCA.ratio) )

#ggplot(subset(qcdata.endo, SampleType == 'BE'), aes(ASCAT.SCA.ratio_max, Purity_max)) + geom_point() + facet_grid(~Status) + geom_hline(yintercept = 0.95)  + geom_vline(xintercept = 0.001)

lowsca = subset(qcdata.endo, SampleType == 'BE' & ASCAT.SCA.ratio_max <= 0.01 & Purity_max > 0.98 )

table(unique(lowsca[,c('PatientID','Status')])$Status)/table(unique(qcdata.endo[,c('PatientID','Status')])$Status)

table(unique(subset(qcdata.endo, SampleType == 'BE' & ASCAT.SCA.ratio_max <= 0.001, select=c('PatientID','Status')))$Status)

ggplot(subset(qcdata.endo,SampleType == 'BE'), aes(Status, ASCAT.SCA.ratio_max, group=Status)) + geom_boxplot() + geom_hline(yintercept = 0.002, color='red')

qcdata %>% dplyr::group_by( Status, SampleType) %>% dplyr::summarise( median(ASCAT.SCA.ratio))

@@

@@

# Adjust for ploidy
for (i in 1:nrow(mergedSegs)) {
  sample = rownames(mergedSegs)[i]
  x = unlist(strsplit(sample, '_'))
  #ploidy = mean(subset(qcdata, SampleType == 'BE' & PatientID == x[1] & EndoID == x[2])$Ploidy)
  ploidy = subset(qcdata.endo, PatientID == x[1] & EndoID == x[2] & SampleType == 'BE')$Ploidy_mean
  if (grepl('BLD|gastric', sample, ignore.case = T)) ploidy = 2
  mergedSegs[i,] = mergedSegs[i,]-(ploidy-1)
  mergedArms[i,] = mergedArms[i,]-(ploidy-1)
}

@@

@@

```{r, warning=F, fig.height=8}
#qcdata.be = subset(qcdata, SampleType == 'BE')
# get.qcinfo<-function(vec) {
#   endo = vec[2]
#   pt = vec[1]
#   y = subset(qcdata.be, PatientID == pt & EndoID == endo)
#   y = y %>% group_by(Status, Timepoint) %>%  dplyr::summarise( mean(Ploidy), mean(Purity), mean(Goodnessoffit), mean(SCA.Ratio) )
#   cbind.data.frame('PatientID'=pt, 'EndoID'=endo, y, stringsAsFactors = F)
# }
preds = preds %>% dplyr::group_by(Samplename) %>% dplyr::mutate(
  PatientID = unlist(strsplit(Samplename,'_'))[1],
  EndoID = unlist(strsplit(Samplename,'_'))[2]
)

pred.qc = merge(preds,qcdata.endo, by=c('PatientID','EndoID'))

#dim(pred.qc)
#table(pred.qc$Status)

grid.arrange(
  ggplot(pred.qc, aes(ASCAT.SCA.ratio_mean, Prob, color=Status)) + geom_point(),
  ggplot(pred.qc, aes(Ploidy_max, Prob, color=Status)) + geom_point(),
ncol=2)

pander(cor.test(pred.qc$ASCAT.SCA.ratio_mean, pred.qc$Prob))
```

@@

pred.qc = pred.qc %>% group_by(Status, PatientID) %>% dplyr::mutate(
  exclude=(Status == 'NP' & (length(which(Pathology == 'HGD')) > 0)),
  wgd = (Status == 'NP' & Ploidy_max > 2.7 )
)

@@

pred.qc = pred.qc %>% group_by(Status, Samplename) %>% dplyr::mutate(
  lowsca = ( ASCAT.SCA.ratio_mean < 0.02 & Purity_mean > 0.95)
)

ggplot(pred.qc, aes(ASCAT.SCA.ratio_mean, Purity_mean, color=lowsca)) + geom_point() + facet_grid(~Status) + 
  geom_vline(xintercept=0.02) + geom_hline(yintercept = 0.95)

pander(
  rbind(rbind('n.Samples'=table(subset(pred.qc, !lowsca )$Status)),
  rbind('n.Patients'=table(unique(subset(pred.qc, !lowsca, select=c('PatientID','Status')))$Status))),
caption='Number of samples and patients that pass the low SCA:high purity thresholds')

pander(
  rbind(rbind('n.Samples'=table(subset(pred.qc, !lowsca & !exclude & !wgd)$Status)),
  rbind('n.Patients'=table(unique(subset(pred.qc, !lowsca  & !exclude & !wgd, select=c('PatientID','Status')))$Status))),
caption='Number of samples and patients that pass the low SCA:high purity & NP thresholds')

@@

```{r echo=F}
pred.qc.ex = subset(pred.qc, SampleType == 'BE' & !exclude & !wgd & !lowsca)
cuts = seq(0,1,0.1)

@@

norm.pred = subset(pred.qc, SampleType != 'BE')

pred.qc = subset(pred.qc, SampleType == 'BE')

@@

@@

@@

ggplot(subset(pred.qc, !exclude & !wgd & !lowsca), aes(ASCAT.SCA.ratio_mean,Prob, color=Risk, shape=Status)) + 
  facet_grid(~Status) + geom_point()

@@

write.table(subset(pred.qc, lowsca, select=c('PatientID','EndoID','Status','ASCAT.SCA.ratio_mean','SCA.Ratio_mean','Purity_mean')),
            sep='\t', quote=F, row.names=F, file='lowsca_pts.txt')

head(qcdata)

x = subset(qcdata, ASCAT.SCA.ratio < 0.02 & Purity > 0.95)
table(x$SampleType)/table(qcdata$SampleType)

write.table(subset(x, SampleType == 'BE', select=c('PatientID','EndoID','Samplename','ASCAT.SCA.ratio','SCA.Ratio','Purity')), quote=F, sep='\t', row.names = F, file='lowsca_samples.txt')

#x = subset(qcdata, ASCAT.SCA.ratio < 0.02 & Purity > 0.95 & SampleType == 'BE')

@@

ct = cor.test(pred.qc.ex$Prob, pred.qc.ex$ASCAT.SCA.ratio_mean)
ct2 = cor.test(pred.qc$Prob, pred.qc$ASCAT.SCA.ratio_mean)
```

@@

```{r loo, eval=T}
